Estimating individual subjective values of emotion regulation strategies

### 2022-02-22 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
cross referenced supplement
added flexER scale

## Detailed information on psychometric measures

@@

>>>>

## Detailed information on psychometric measures {#SupplementQuestionnaires}

@@

*Emotion regulation flexibility.*
Flexible use of ER strategies was assessed using the FlexER Scale [@Doerfel2019] with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which are answered on a 4-point scale ranging from "strongly agree" to "strongly disagree".
Psychometric properties are currently under investigation.
